### 2024-11-10 README.Rmd
find_nearest() support new_data in various formats
+ print/format support for single-row and single column embeddings
+ embeddings coercion for numeric vectors

```{r}
library(dplyr)
valence_df <- tribble(
	~id,        ~text,
	"positive", "happy awesome cool nice",
	"neutral",  "ok fine sure whatever",
	"negative", "sad bad horrible angry"
	)

>>>>

```{r, warning=FALSE, message=FALSE}
library(dplyr)
valence_df <- tribble(
	~id,        ~text,
	"positive", "happy awesome cool nice",
	"neutral",  "ok fine sure whatever",
	"negative", "sad bad horrible angry"
	)
